Twisted 11-dimensional supergravity, I

### 2021-08-06 draft.tex
stuff merge

%check CME

>>>>

\parsec
%check CME
We now specialize to the case where $X$ is an odd Calabi--Yau manifold and $L$ an odd-dimensional smooth manifold. 
In this case, there exists a consistent deformation of the BF theory we have constructed by a further term which is not of BF type. That is, we cannot define this deformation at the level of the local $L_\infty$ algebra resolving divergence-free holomorphic vector fields; it is defined only at the level of the full BF theory.

Recall that such deformations are governed by the classical master equation: the parameterized family of actions $I + \alpha J$ is sensible only if 
\deq{
  \{I+ \alpha J, I + \alpha J \} = 0.
}
Since this must hold for all $\alpha$, and since the undeformed action $I$ is already a solution to the classical master equation, this reduces to the two conditions 
\deq[eq:2cond]{
  \{I,J\} = \{J,J\} = 0.
}
\begin{thm}
  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, I_\infty)$ on $X \times L$ constructed above. The local functional 
  \deq{
    J = \gamma (\del \gamma)^k,
  }
  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,I_\infty)$ as a $\Z/2\Z$-graded BV theory.
\end{thm}
\begin{proof}
  First off, we consider grading issues. In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$. The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$. As such, we have
  \deq{
    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
  }
  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.

  We then consider the classical master equation, in the form of the conditions~\eqref{eq:2cond}. It is immediate from the form of the shifted Poisson bracket that $\{J,J\} = 0$, since $J$ depends only on the $\gamma$ field. It remains to check that $\{I_\infty,J\} = 0$. For the quadratic term, we note that 
  \deq{
    \{\beta\div\mu, J\} = (k+1) \del\beta (\del \gamma)^k = 0,
  }
  because total derivatives are equivalent to zero as local functionals. The cubic term takes the form
  \deq{
    \left\{ \frac{1}{1-\nu} \del\gamma \mu^2, \gamma(\del\gamma)^k \right\} = \frac{2(k+1)}{1-\nu} (\del\gamma\vee\mu) (\del\gamma)^k.
}
This expression is zero for symmetry reasons. Recall that $\del\gamma$ is a two-form, and that the expression must be a totally symmetric local functional in $(k+1)$ copies of this two-form. We can ask whether such a  contraction exists just at the level of $\lie{sl}(2k+1)$ representation theory by computing the decomposition of the two-form  
\end{proof}
